---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ghooks

<!-- badges: start -->
<!-- badges: end -->

The goal of `{ghooks}` is to provide `{ghooks}` hooks for standard `{shiny}` apps.

## Installation

You can install the development version of `{ghooks}` like so:

``` r
pak::pak("thinkr-open/ghooks")
```

## `{golem}` hooks

`{golem}` hooks are functions that are called by `{golem}` at specific moments of the app lifecycle.
They are used to add custom code to the app, notably when creating the app with `create_golem()`.

You can find more info about `{golem}` hooks on [`{golem}` documentation](https://thinkr-open.github.io/golem/articles/f_extending_golem.html).

The hooks can be called with `golem::create_golem(project_hook = )`, when creating a new golem project via the RStudio widget, as show on the screenshot in the [Extending `{golem}`](https://thinkr-open.github.io/golem/articles/f_extending_golem.html#defining-your-own-project_hook) Vignette.

Below is the list of curently available hooks:

### `geyser_hook`

This hook is mainly intended at demoing the `{golem}` hooks system.
It adds the "Old Faithful Geyser Data" app to your golem project.

```{r}
pth <- tempfile(pattern = "geyser")
old_wd <- getwd()
unlink(pth, recursive = TRUE)
golem::create_golem(
  pth,
  project_hook = ghooks::geyser_hook,
  open = FALSE
)
```


<details>
<summary>Click here to see the content of `app_ui` and `app_server`</summary>

```{r}
cat(
  readLines(
    file.path(pth, "R", "app_ui.R")
  ),
  sep = "\n"
)
```

```{r}
cat(
  readLines(
    file.path(pth, "R", "app_server.R")
  ),
  sep = "\n"
)
```

</details>

## About

You're reading the doc about version : `r pkgload::pkg_version()`

This README has been compiled on:

```{r}
Sys.time()
```

Here are the test & coverage results :

```{r}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("ghooks")
```

```{r}
covr::package_coverage()
```


